Global well-being and mental health in the internet age

### 2022-07-14 Analysis.qmd
Table of ITU aggregates

>>>>

```{r itu-aggregates}
#| tbl-cap: "ITU's reported percentages of World's individuals using the internet"
#| label: tbl-ituworld

if (!file.exists(here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))) {
  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))
}
# Individuals using the internet per 100 inhabitants | World
tmp <- read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
tmp %>% 
  kbl() %>% 
  kable_custom()
```
